R Project: Chapter 14
Baker, Ceridwen
Math M15H, Fall 2020
```{r}
# Load the germane libraries
library(tidyverse)
```

```{r}
library(faraway)
```

```{r}
# Load and check out the data from the Faraway package.
dat <- data.frame(uswages)
glimpse(dat)
```
```{r}
view(dat)
```

1a. Create a scatterplot with the regression line for experience vs. wage.
```{r}
ggplot(data=dat, aes(x=exper, y=wage))+geom_point()+geom_smooth(method = lm)
```

1b. Create a scatterplot with the regression line for education vs. wage.
```{r}
ggplot(data=dat, aes(x=educ, y=wage))+geom_point()+geom_smooth(method = lm)

```

2a. Save the linear model for wage ~ experience as mod1.
```{r}
mod1 <- lm(wage ~ exper, data=dat)
mod1
```

2b. Save the summary of mod1 as mod1_sum. Print the summary.
```{r}
mod1_sum <- summary(mod1)
mod1_sum
```

3a. Save the linear model for wage ~ education as mod2.
```{r}
mod2 <- lm(wage ~ educ, data=dat)
mod2
```

3b. Save the summary of mod2 as mod2_sum. Print the summary.
```{r}
mod2_sum <- summary(mod2)
mod2_sum
```

4a. Now create a quadratic regression curve for experience and wage. Call this mod3. Print the summary.
```{r}
mod3 <- lm(wage ~ I(exper^2) + I(exper),dat)
summary(mod3)
```

4b. Does having the quadratic term help give a better model? Explain and justify your answer.
The quadratic has a better model because the goodness of fit is better in the quadratic than in the linear. the linear has a 0.033 and the quadratic has a 0.098.

5a. Now create a model with education and wage as predictors and wage as the response variable. Call this mod4. Print its summary.
```{r}
mod4 <- lm(wage ~  educ + wage, dat)
summary(mod4)
```

5b. Now create a model with education and experience as predictors and wage as the response variable. Also include an interaction variable of education and experience. Call this mod5. Print its summary.
```{r}
mod5 <- lm(wage ~  educ + exper, dat)
summary(mod5)
```

6. Please rank mod1, mod2, mod3, mod4, and mod5 from best to worst. Explain and justify your answer in detail. 

1.mod5
2.mod3
3.mod2
4.mod1
5.mod4
mod 4 dosent make sence because having wage as a predictor and a response variable makes no sense so it is last. I ordered 1-3 ad 5 the way they are based on the r squared value. mod 5 has the largest at .1343 next is mod3 at 0.09822  then mod2 at 0.0612 and then mod1 at 0.03308. 
