R Project: Chapter 13
LAST, FIRST
Math M15H, Fall 2020
```{r}
library(tidyverse)
```
```{r}
library(faraway)
library(smatr)
```

```{r}
# Load and check out the data from the Faraway package.
dat <- data.frame(uswages)
glimpse(dat)
```

1a. Create a scatterplot with the regression line for experience vs. wage.
2.Save the linear model for wage ~ experience as mod1.
3a. Save the summary of mod1 as mod1_sum. Print the summary.
3b. Find the following for mod1: the coefficents of regression line, r, r^2, and std dev of regression line.
3c. Write the regression line with the coefficients from the output in the form y^hat = a + bx.
[Type answer here.]
4a. Plot the residual plot.
####4b. What does the residual plot tell you about the linear model? ##### [Answer here.]

5a. Construct a 95% confidence interval for the slope of the regression line.
5b. Interpret the confidence interval.
[Answer here.]
6a. Perform an equivalent hypothesis test to the confidence interval on the slope of the regression line using the t-distribution.
6b. Interpret the result in reference to the null and alternative hypotheses.
[Answer here.]
7a. Give the first ten confidence intervals for the mean. Hint: Use the following wrapper: head().
7b. Give the first ten prediction intervals.
7c. Which intervals are wider? The confidence intervals for the mean or the prediction intervals? Explain and justify your answer.
[Answer here.]





