R Project: Chapter 13
LAST, FIRST
Math M15H, Fall 2020
```{r}
library(tidyverse)
```
```{r}
library(faraway)
library(smatr)
```

```{r}
# Load and check out the data from the Faraway package.
dat <- data.frame(uswages)
glimpse(dat)
```

1a. Create a scatterplot with the regression line for experience vs. wage.
```{r}
ggplot(data=dat, aes(x=exper, y=wage))+geom_point()+geom_smooth(method = lm)
```

2.Save the linear model for wage ~ experience as mod1.
```{r}
mod1 <- lm(wage ~ exper, data=dat)
mod1
```

3a. Save the summary of mod1 as mod1_sum. Print the summary.
```{r}
mod1_sum <- summary(mod1)
mod1_sum
```

3b. Find the following for mod1: the coefficents of regression line, r, r^2, and std dev of regression line.
```{r}
# r
sqrt(mod1_sum$r.squared)

# r^2
mod1_sum$r.squared

#std dev
sd(mod1_sum$residuals)
```

3c. Write the regression line with the coefficients from the output in the form y^hat = a + bx.
y=6.2981 +492.1669x

4a. Plot the residual plot.
```{r}
plot(mod1$residuals)
abline(h=0)

```

####4b. What does the residual plot tell you about the linear model? ##### the linear model is a fairly good fit for the data. the outliers are concerning 

5a. Construct a 95% confidence interval for the slope of the regression line.
```{r}
confint(mod1, level = 0.95)
```

5b. Interpret the confidence interval.
95% chance that there is a relationship between the 2 variables because the 95% confidence interval excludes 0.

6a. Perform an equivalent hypothesis test to the confidence interval on the slope of the regression line using the t-distribution.
```{r}
slope.test(dat$wage, dat$exper, test.value = 0, method = 'OLS', alpha = 0.05)
```
```{r}
t<- 6.298091/6.2981
t
```
```{r}
p <-  2*pt(-abs(t),df=8)
p
```

6b. Interpret the result in reference to the null and alternative hypotheses.
p value is larger than .05 so we fail to reject the null. the slope can be due to chance. 
Ho: beta = 0 OR rho = 0 OR independent OR uncorrelated
Ha: beta not= 0 OR rho not= 0 OR dependent OR correlated

7a. Give the first ten confidence intervals for the mean. Hint: Use the following wrapper: head().
```{r}
 head(predict(mod1, dat, interval = 'confidence'),10)

```

7b. Give the first ten prediction intervals.
```{r}
head(predict(mod1, dat, interval = 'predict'),10)

```

7c. Which intervals are wider? The confidence intervals for the mean or the prediction intervals? Explain and justify your answer.
Predict is far wider from -281.4503 to 1492.515, where as confidence is 585.6946 to 625.3704. 
the predicted is wider because it includes values from the entirety of possible slopes. 
